NIHAO VII: Predictions for the galactic baryon budget in dwarf to Milky Way mass haloes

### 2016-09-12 ms_nihao_budget.tex
enlarge the axis label and reproduce the comparason figure

{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
simulation code and didn't only reproduce the stellar mass - halo mass
relation but also showed a similar baryon fraction relation, e.g. in 
L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
This suggests that the potential well of the halo regulates the baryon
fraction.
Meanwhile, \citet{Voort16} have similar result produced by zoom-in 
cosmological hydrodynamic simulation suit FIRE which has 16 galaxies 
with similar halo mass range.
Fig.~\ref{fig:fire_com} compares baryon and stellar fraction with 
\citet{Voort16} and \citet{Christensen}, we derive
new baryonic mass and stellar mass within R$_{500}$ and R$_{100}$
to make sure the ratios compared in each panel have same definitions with
ratios from other simulation suites. The baryon fraction in NIHAO simulations
have good agreement with both of the simulation suite in the whole mass range
where NIHAO simulations explored. For the massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.
For stellar fraction, \citet{Voort16} shows a almost same result with
our work, even at low mass range, the two galaixes may suggest the 
large scatter as we produced.}

>>>>

{\bf \citet{Christensen16} run twenty galaxy simulations spanning the mass range
from $10^{9.5} - 10^{12} \Msun$ using zoom-in cosmological hydrodynamic 
simulation code and didn't only reproduce the stellar mass - halo mass
relation but also showed a similar baryon fraction relation, e.g. in 
L$^*$ galaxies, the fraction is reduced by 20\% while in galaxies with
halo mass $< 10^{10} \Msun$ there can be as large as an 80\% mass reduction.
This suggests that the potential well of the halo regulates the baryon
fraction.
Meanwhile, \citet{Voort16} have similar result produced by zoom-in 
cosmological hydrodynamic simulation suit FIRE which has 16 galaxies 
with similar halo mass range.
Fig.~\ref{fig:fire_com} compares baryon and stellar fraction with 
\citet{Voort16} and \citet{Christensen16}, we derive
new baryonic mass and stellar mass within R$_{500}$ and R$_{100}$
to make sure the ratios compared in each panel have same definitions with
ratios from other simulation suites. The baryon fraction in NIHAO simulations
have good agreement with both of the simulation suite in the whole mass range
where NIHAO simulations explored. The massive haloes with 
M$_{500} > 10^{12} \Msun$, there are two galaxies from NIHAO have
reduced baryon fraction and four more massive galaxies from FIRE
have larger reduced baryon fraction which may hint that the baryon
fraction will decrease as the halo mass increases in large mass range.
For stellar fraction, \citet{Voort16} shows a almost same result with
our work, even at low mass range, the two galaixes may suggest the 
large scatter as we produced. However, \citet{Christensen16} predicts
one magnitude higher stellar fraction than what we found at the halo 
mass range belowe $10^{11.5} \Msun$, which is expected by the
comparason with abundance-matching-derived fits shown in Fig. 3 in
their paper.}
